Data Exploration: IUCN and AquaMaps

### 2015-09-04 data_explore.Rmd
added regression

reg <- ggplot(spp_list, aes(sm_perc,total_area,color=sm_range)) + geom_point() + geom_abline() + labs(y='Total Area', x='Percent overlap smaller range in larger', title='Comparing differences in area across species groups', fill='IUCN Category')

@@

model = lm(spp_list$total_area~spp_list$sm_perc)
summary(model)

>>>>

reg <- ggplot(spp_list, aes(sm_perc,total_area,color=sm_range)) + geom_point() + geom_abline() + labs(y='Total Area (km2)', x='Percent overlap smaller range in larger', title='Size of species range vs. percent overlap of \nsmaller range with larger')

@@

# remove all area greater than 100000000

l = spp_list%>%filter(total_area <100000000)

r <- ggplot(l, aes(sm_perc,total_area,color=sm_range)) + geom_point() + labs(y='Total Area (km2)', x='Percent overlap smaller range in larger', title='Size of species range vs. percent overlap of \nsmaller range with larger')

print(r)

#-----

# Regression

lm_eqn <- function(df){
    m <- lm(total_area ~ sm_perc, spp_list);
    eq <- substitute(italic('Total Area') == a + b %.% italic('Percent')*","~~italic(r)^2~"="~r2, 
         list(a = format(coef(m)[1], digits = 2), 
              b = format(coef(m)[2], digits = 2), 
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));                 
}

p1 <- reg + geom_text(x = 50, y = 80000000, label = lm_eqn(spp_list), parse = TRUE)
